Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 theory.tex
includes new references

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mueller1994,Ji1997a,Radyushkin1996} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{2009a,2010,CollaborationPhys.Rev.D75:0111032007,HERMEScollaboration2010,HERMESCollaborationPhys.Rev.Lett.87:1820012001} on
the leptoproduction of real photons from a nucleon that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD \blue{that} describes a soft part of the scattering
process.

@@

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{$\gamma^\ast$)}. The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}. The quark is absorbed by the nucleon with fraction $x-\xi$. Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

@@

The differential four-fold cross section for the leptoproduction of real photons
from an unpolarised target can be written \cite{Belitsky2002}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the nucleon mass and $\phi$ is the
azimuthal angle between the scattering and production planes REF\_TRENTO.
The scattering amplitude $\tau$ can be written
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and the interference term (I). These
contributions can be written 
\begin{equation}
 |\tau_{\textrm{BH}}|^{2} =
\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\left(c_{0}^{
\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
\label{e:tbh}
\end{equation}
\begin{equation}
 \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1}^{\textrm{DVCS}}\sin\phi\right),
\label{e:tdvcs}
\end{equation}
\begin{equation}
\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
I}}
+
\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)\right),
\label{e:ti}
\end{equation}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process and $\lambda$ and $e_\ell$ are respectively the
helicity and unit charge of the lepton beam.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_n^V,s_n^W$]
\blue{(}$V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$\blue{)} can be
found in
Ref.~\cite{Belitsky2002}.

This paper provides a set of results analogous to those reported in
Ref.~\cite{2009a}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment \blue{(i.e. uses a missing-mass technique for event selection)}, but represent the largest DVCS data set that will
be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
the reader is referred to Ref.~\cite{2009a}.

There are two sets of asymmetries that are measured at H{\sc
ermes} with an unpolarised target and a polarised electron or positron beam:
beam-helicity asymmetries and beam-charge asymmetries. It is possible to
disentangle the DVCS and interference contributions to the beam-helicity
asymmetry due to the beam-charge dependence of the interference term, so that
this paper, as Ref.~\cite{2009a}, presents results on the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air06,Air08,Air09,Air10,Air10a} on
the leptoproduction of real photons from a nucleon that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD \blue{that} describes a soft part of the scattering
process.

@@

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}. The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}. The quark is absorbed by the nucleon with fraction $x-\xi$. Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

@@

The differential four-fold cross section for the leptoproduction of real photons
from an unpolarised target can be written \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the nucleon mass and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The scattering amplitude $\tau$ can be written
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and the interference term (I). These
contributions can be written 
\begin{equation}
 |\tau_{\textrm{BH}}|^{2} =
\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\left(c_{0}^{
\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
\label{e:tbh}
\end{equation}
\begin{equation}
 \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1}^{\textrm{DVCS}}\sin\phi\right),
\label{e:tdvcs}
\end{equation}
\begin{equation}
\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
I}}
+
\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)\right),
\label{e:ti}
\end{equation}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process and $\lambda$ and $e_\ell$ are respectively the
helicity and unit charge of the lepton beam.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_n^V,s_n^W$]
\blue{(}$V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$\blue{)} can be
found in
Ref.~\cite{Bel02b}.

This paper provides a set of results analogous to those reported in
Ref.~\cite{Air09}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment \blue{(i.e. uses a missing-mass technique for event selection)}, but represent the largest DVCS data set that will
be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
the reader is referred to Ref.~\cite{Air09}.

There are two sets of asymmetries that are measured at H{\sc
ermes} with an unpolarised target and a polarised electron or positron beam:
beam-helicity asymmetries and beam-charge asymmetries. It is possible to
disentangle the DVCS and interference contributions to the beam-helicity
asymmetry due to the beam-charge dependence of the interference term, so that
this paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}
